A GPU Sonar Simulator for Automatic Target Recognition

### 2014-05-09 Simulator/article.tex
la2pdf commit - 2014:05:08	12:03:57	(Thu 8.May)
la2pdf commit - 2014:05:08	18:06:57	(Thu 8.May)
la2pdf commit - 2014:05:09	10:43:41	(Fri 9.May)

@@

% \appendices
% 
% \section{MVDR Complexity Formulas}\label{mvdr_formulas}
% 
% \section{GPU Throughput}\label{throughput}
% 
% bs bs

>>>>

\begin{align*}
\left(\begin{matrix}
x_c \\ y_c \\ z_c \\ w_c
\end{matrix}\right)
= \left(\begin{matrix}
\frac{2}{r-l}  &  0              &  0              &  -\frac{r+l}{r-l} \\
0              &  \frac{2}{t-b}  &  0              &  -\frac{t+b}{t-b} \\
0              &  0              &  \frac{-2}{f-n} &  -\frac{f+n}{f-n} \\
0              &  0              &  0              &  1
\end{matrix}\right)
\left(\begin{matrix}
x_e \\ y_e \\ z_e \\ w_e
\end{matrix}\right)
\end{align*}
where
\begin{align*}
l &=   &  r &= \\
b &=   &  t &= \\
f &=   &  n &= 
\end{align*}

@@

\appendix

We implement rotations in a 3D euclidean space by combining matrices that rotate around each of the three respective dimensions.. For rotation by an angle $\phi_x$ clockwise around the $x$-axis we have:
\begin{align}
\R_x(\phi_x) &= \bmat{
1  &  0           &  0           &  0 \\
0  &  \cos\phi_x  &  -\sin\phi_x &  0 \\
0  &  \sin\phi_x  &  \cos\phi_x  &  0 \\
0  &  0           &  0           &  1 \\
},
\end{align}
and for the other two euclidean dimensions we have:
\begin{align}
\R_y(\phi_y) &= \bmat{
\cos\phi_y  &  0  &  \sin\phi_y  &  0 \\
0           &  1  &  0           &  0 \\
-\sin\phi_y &  0  &  \cos\phi_y  &  0 \\
0           &  0  &  0           &  1 \\
},
\end{align}
and
\begin{align}
\R_z(\phi_z) &= \bmat{
\cos\phi_z  &  -\sin\phi_z &  0  &  0 \\
\sin\phi_z  &  \cos\phi_z  &  0  &  0 \\
0           &  0           &  1  &  0 \\
0           &  0           &  0  &  1 \\
}.
\end{align}
The order in which these are applied matters. We rotate around the $x$-axis first, then around $y$ and finally around $z$:
\begin{align}
\R(\phi_x, \phi_y, \phi_z) &= \R_z(\phi_z)\;\R_y(\phi_y)\;\R_x(\phi_x).
\end{align}

\begin{align}
\boldsymbol{T} &= \bmat{
1  &  0  &  0  &  dx \\
0  &  1  &  0  &  dy \\
0  &  0  &  1  &  dz \\
0  &  0  &  0  &  1 \\
}
\end{align}

\begin{align}
\boldsymbol{S} &= \bmat{
s_x  &  0    &  0    &  1 \\
0    &  s_y  &  0    &  1 \\
0    &  0    &  s_z  &  1 \\
0    &  0    &  0    &  1 \\
}
\end{align}

% \section{MVDR Complexity Formulas}\label{mvdr_formulas}
% 
% \section{GPU Throughput}\label{throughput}
% 
% bs bs
